Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere

### 2020-12-09 paper/dcpo_gender_roles.Rmd
revise covergent validation paragraph for length, keeping more detailed description in comments for convenient reference just in case

# Validating Public Gender Egalitarianism
We turn now to the validity of the PGE Mean scores.
Like @Caughey2019 [684-685], we provide evidence of our new measure's validity through tests of both convergent validation and construct validation.

@@

Figure&nbsp;\ref{conv_plot} displays our tests of convergent validation.
Convergent validation refers to demonstrating that a measure is empirically associated with alternative indicators of the same concept [@Adcock2001, 540].
Here, we compare PGE Mean scores to responses to individual survey items that were included in the source data, that is, we provide an "internal" validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years, combining for this purpose all those who agreed or strongly agreed that "on the whole, men make better political leaders than women."
Then, in the center panel, we look at the question that provides most data-rich cross-section: the `poliequal3` item in Pew Global's Spring 2007 survey that asked whether respondents felt "men generally make better political leaders than women," vice versa, or whether "in general, women and men make equally good political leaders."
Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country.
The U.S. General Social Survey asked this question 25 times from 1972 to 2016.
It asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women"; to facilitate visual comparison of the longitudinal relationship, we plot the estimated population proportion that disagreed with the statement.
In every case, the correlations---estimated taking into account the uncertainty in the measures^[The uncertainty in the PGE Mean score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the `polileader4` question, but failing to account for this uncertainty would overstate the correlation with the Pew `poliequal3` item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S. GSS `emopoli2` item, at $R =$ `r with(internal_us, cor(prop, mean, use = "pairwise.complete.obs")) %>% round(2)`.
We take up the issue of the importance of taking uncertainty into account when working with the PGE data in a subsequent section.]---are in the expected direction and very strong.

@@

In Figure&nbsp;\ref{surv_const_plot}, we move on to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
For purposes of construct validation, we look first to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
Although many of the items in this category are on their face at best only very tangentially related to public gender egalitarianism, others are plausibly causally related.
Consider `wantch4`, an item depicted in the left pane asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children."
As agreement suggests that women do not truly care about opportunities in the workplace, those who do should be expected to be less likely to believe women should enjoy equal access to such opportunities which men implicitly value more.
Or, similarly, `familywoman4`, an item plotted in the center pane from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family." 
Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
(Indeed, the `tradroles` series of questions, which couple the `familywoman4` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.)
If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
In either case, though, they provide evidence of the validity of the PGE Mean scores.]
In a slightly different vein, `preschoolwork4`, included in the German ALLBUS, the World Values Survey, and the European Values Survey, asked respondents the extent to which they agreed that "a pre-school child is likely to suffer if his or her mother works;" we plot the time series of the proportion of the population of Germany estimated to disagree or disagree strongly with this statement in the right pane.
The belief that mothers working cause harm to their children should be expected to lead to disfavoring gender equality in workforce to avoid this purported negative consequence. 
With regard to all of these items, too, the correlations with the PGE Mean scores are strong.

@@

Figure&nbsp;\ref{construct_plot} shows our tests of construct validation.
Construct validation refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
Assuming that attitudes toward gender egalitarianism in the public sphere both cause and are caused by women's gains in the workplace, assessing the relationships between the mean PGE and measures of workplace gender equality provides construct validation of our measure.
In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the mean PGE index to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2016))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
In the right panel, we plot the mean PGE index against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].
Both correlations are strong.
As with our tests of convergent validation, these tests of construct validation provide reassuring evidence of the validity of the mean PGE.

>>>>

# Validating Public Gender Egalitarianism
We consider now the validity of the PGE Mean scores.
Like @Caughey2019 [684-685], we provide evidence of our new measures' validity with both convergent validation and construct validation tests.

@@

Figure&nbsp;\ref{conv_plot} displays our tests of convergent validation.
Convergent validation refers to demonstrating that a measure is empirically associated with alternative indicators of the same concept [@Adcock2001, 540].
Here, we compare PGE Mean scores to responses to individual survey items that were included in the source data, that is, we provide an "internal" validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years.
<!-- In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years, combining for this purpose all those who agreed or strongly agreed that "on the whole, men make better political leaders than women." -->
Then, in the center panel, we look at the question that provides most data-rich cross-section.
<!-- Then, in the center panel, we look at the question that provides most data-rich cross-section: the `poliequal3` item in Pew Global's Spring 2007 survey that asked whether respondents felt "men generally make better political leaders than women," vice versa, or whether "in general, women and men make equally good political leaders." -->
Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the item with the largest number of observations for a single country. 
<!-- Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country. -->
<!-- The U.S. General Social Survey asked this question 25 times from 1972 to 2016. -->
<!-- It asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women"; to facilitate visual comparison of the longitudinal relationship, we plot the estimated population proportion that disagreed with the statement. -->
In every case, the correlations---estimated taking into account the uncertainty in the measures^[The uncertainty in the PGE Mean score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the `polileader4` question, but failing to account for this uncertainty would overstate the correlation with the Pew `poliequal3` item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S. GSS `emopoli2` item, at $R =$ `r with(internal_us, cor(prop, mean, use = "pairwise.complete.obs")) %>% round(2)`.
We take up the issue of the importance of taking uncertainty into account when working with the PGE data in a subsequent section.]---are in the expected direction and very strong.

@@

In Figure&nbsp;\ref{surv_const_plot}, we turn to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
For purposes of construct validation, we look first to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
Although many of the items in this category are on their face at best only very tangentially related to public gender egalitarianism, others are plausibly causally related.
Consider `wantch4`, an item depicted in the left pane asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children."
As agreement suggests that women do not truly care about opportunities in the workplace, those who do should be expected to be less likely to believe women should enjoy equal access to such opportunities which men implicitly value more.
Or, similarly, `familywoman4`, an item plotted in the center pane from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family." 
Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
(Indeed, the `tradroles` series of questions, which couple the `familywoman4` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.)
If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
In either case, though, they provide evidence of the validity of the PGE Mean scores.]
In a slightly different vein, `preschoolwork4`, included in the German ALLBUS, the World Values Survey, and the European Values Survey, asked respondents the extent to which they agreed that "a pre-school child is likely to suffer if his or her mother works;" we plot the time series of the proportion of the population of Germany estimated to disagree or disagree strongly with this statement in the right pane.
The belief that mothers working cause harm to their children should be expected to lead to disfavoring gender equality in workforce to avoid this purported negative consequence. 
With regard to all of these items, too, the correlations with the PGE Mean scores are strong.

@@

Figure&nbsp;\ref{construct_plot} shows additional tests of construct validation.
Assuming that attitudes toward gender egalitarianism in the public sphere both cause and are caused by women's gains in the workplace, assessing the relationships between the mean PGE and measures of workplace gender equality provides construct validation of our measure.
In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the mean PGE index to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2016))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
In the right panel, we plot the mean PGE index against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].
Both correlations are strong.
As with our tests of convergent validation, these tests of construct validation provide reassuring evidence of the validity of the mean PGE.
